Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Added some exercises

>>>>

\begin{enumerate}
\item Figure~\ref{fig:incenter} shows an attempt at trying to fix the code of
    Figure~\ref{fig:inc}.  Run it through CXL and see what happens.  Based on
    the error output, Describe in English what is wrong with the code by describing,
    in broad steps, how running the program can get into a bad state.
\item What if we moved line~2 of Figure~\ref{fig:incenter} to after the \texttt{if}
    statement (between lines~7 and~8)?  Do you think that would work?  Run it through
    CXL and describe either why it works or why it does not work.
\end{enumerate}
